<!--
%\VignetteEngine{knitr::knitr}
%\VignetteIndexEntry{Display Tables with the DataTables Library}
-->

# jQuery DataTables

We can use the JavaScript library [`DataTables`](http://www.datatables.net) to generate enhanced tables in HTML. In the example below, we create a table for the `mtcars` data:

```{r cool, results='asis'}
library(knitr)
kable(mtcars, 'html', table.attr='id="mtcars_table"')
```

Note we assigned an `id` to the table, and next we use the `DataTables` library to tweak the table.

```js
<script type="text/javascript" charset="utf-8">
	$(document).ready(function() {
		$('#mtcars_table').dataTable();
	} );
</script>
```

<script type="text/javascript" charset="utf-8">
  $(document).ready(function() {
		$('#mtcars_table').dataTable();
	} );
</script>

Since this is a Markdown vignette, we need to add the JavaScript libraries as well as some additional CSS files to the HTML header, and this can be done via:

```{r}
options(markdown.HTML.header = system.file('misc', 'datatables.html', package = 'knitr'))
```

Two files `vignette.css` and `datatables.html` under the `misc` directory of **knitr** were added to the HTML output.

By comparison, below is an ordinary table:

```{r boring, results='asis'}
kable(head(mtcars), 'html')
```
