<!--
%\VignetteEngine{knitr::docco_linear}
%\VignetteIndexEntry{R Markdown with the Docco Linear Style}
-->

# R Markdown with the Docco Linear Style

This is an example of Markdown vignettes using the [Docco style](http://ashkenas.com/docco/).

## Docco

To use the Docco style for Markdown vignettes in an R package, you need to

- add `*.Rmd` files under the `vignettes` directory
- add `Suggests: knitr` and `VignetteBuilder: knitr` to the `DESCRIPTION` file
- specify the vignette engine `\VignetteEngine{knitr::docco_linear}` in the `Rmd` files (inside HTML comments)

After building and installing the package, you can view vignettes via

```r
browseVignettes(package = 'Your_Package')
```

## Examples

Below are some code chunks as examples.

```{r hello, results='asis'}
cat('_hello_ **markdown**!', '\n')
```

Normally you do not need any chunk options.

```{r}
1+1
10:1
rnorm(5)^2
strsplit('hello, markdown vignettes', '')
```

Feel free to draw beautiful plots and write math $P(X>x)=\alpha/2$.

```{r}
n=300; set.seed(123)
par(mar=c(4,4,.1,.1))
plot(rnorm(n), rnorm(n), pch=21, cex=5*runif(n), col='white', bg='gray')
```

## How does it work

The **markdown** package (>= v0.6.2) supports custom HTML templates, and the `docco` engine in **knitr** uses a custom template to compile Markdown to HTML:

```{r header, eval=FALSE}
knit2html(..., template = system.file('misc', 'docco-template.html', package='knitr'))
```

That is it.
