---
title: "Not An Introduction to knitr"
author: "Yihui Xie"
date: "`r Sys.Date()`"
output:
  markdown::html_format:
    meta:
      css: ["@default", "@prism-xcode"]
      js: ["@npm/@xiee/utils/js/center-img.min.js"]
vignette: >
  %\VignetteEngine{knitr::knitr}
  %\VignetteIndexEntry{Not an Introduction to knitr}
---

The **knitr** package is an alternative tool to Sweave based on a different
design with more features. This document is not an introduction, but only serves
as a placeholder to guide you to the real manuals, which are available on the
package website <https://yihui.org/knitr/> (e.g. the [main
manual](https://yihui.org/knitr/demo/manual/) and the [graphics
manual](https://yihui.org/knitr/demo/graphics/) ), and remember to read the help
pages of functions in this package. There is a book "Dynamic Docuemnts with R
and knitr" for this package, too.

Anyway, here is a code chunk that shows you can compile vignettes with **knitr**
as well using R 3.0.x, which supports non-Sweave vignettes:

```{r show-off, tidy=TRUE}
options(digits=4)
rnorm(20)
fit=lm(dist~speed, data=cars)
b=coef(fit)
```

```{r echo=FALSE}
knitr::kable(summary(fit)$coefficients)
```

The fitted regression equation is $Y=`r b[1]`+`r b[2]`x$.

```{r graphics, fig.cap='A scatterplot with a regression line.'}
par(mar=c(4, 4, 1, .1))
plot(cars, pch = 20)
abline(fit, col = 'red')
```

## References

```{r, echo=FALSE, results='asis', warning=FALSE}
print(citation('knitr'), style = 'html')
```
