This is a minimal example of using **knitr** with in HTML pages. I am actually
using markdown here since it is more convenient in GitHub.

First, the input file was named as `knitr-minimal.Rmd`
([source](https://github.com/yihui/knitr/blob/master/inst/examples/knitr-minimal.Rmd)),
and **knitr** will automatically determine the output filename to be
`knitr-minimal.md` (`*.Rmd --> *.md`).

```{r setup}
# set global chunk options: images will be 5x5 inches
opts_chunk$set(fig.width=5, fig.height=5)
```

Now we write some code chunks in this markdown file:

``` {r}
## a simple calculator
(x <- 1+1)
## boring random numbers
set.seed(123)
rnorm(5)
```

We can also produce plots:

``` {r md-cars-scatter, message=FALSE}
library(ggplot2)
qplot(hp, mpg, data=mtcars)+geom_smooth()
```

Inline R code is also supported, e.g. the value of `x` is `r x`, and 2 times pi
= `r 2*pi`.

So no more hesitation on using GitHub and **knitr**! You just write a minimal
amount of code to get beautiful output on the web.
