`r opts_chunk$set(fig.width=5, fig.height=5, fig.path='ex-out-', cache=TRUE, cache.path='cache/upload-')`
This is an example of using **knitr** with extended markdown (e.g.
[GFM](http://github.github.com/github-flavored-markdown/)) and uploading images
to imgur.com automatically. Note you should set the graphical device to create
images that can be displayed in the web browser, e.g. `dev = 'png'` (it is the
default for markdown output) works but `'pdf'` does not.

First, the input file was named as `knitr-upload.Rmd`
([source](https://github.com/yihui/knitr/blob/master/inst/examples/knitr-upload.Rmd)),
and **knitr** will automatically determine the output filename to be
`knitr-upload.md`. 

I used the code below to make sure **knitr** will upload images.

``` {r setup}
opts_knit$set(upload.fun = imgur_upload) # upload all images to imgur.com
````

Now we write some code chunks in this markdown file:

``` {r}
## a simple calculator
1+1
## boring random numbers
set.seed(123)
rnorm(5)
````

We can also produce plots which are uploaded to imgur.com:

``` {r md-cars, message=FALSE}
library(ggplot2)
qplot(hp, mpg, data=mtcars)+geom_smooth()
ggpcp(mtcars) + geom_line()
````

So **knitr** is ready with GitHub with a single markdown file.
