# Test of other languages in knitr

## Languages

R works, of course.

``` {r test-r, engine='R'}
set.seed(123)
rnorm(5)
```

Can **knitr** deal with other languages? You should have them installed.

### Python

``` {r test-python, engine='python'}
x = 'hello, python world!'
print x
print x.split(' ')
```

### Awk

We need to pass a `file` option to Awk.

``` {r test-awk, engine='awk', file=system.file('examples', 'knitr-manual.Rnw', package = 'knitr')}
# how many non-empty lines?
NF {
  i = i + 1
}
END { print i }
```

### Ruby

``` {r test-ruby, engine='ruby'}
x = 'hello, ruby world!'
p x.split(' ')
```

### Haskell

``` {r test-haskell, engine='haskell'}
[x | x <- [1..10], odd x]
```

## Chunk Options

You can use some chunk options like `eval`, `echo` and `results`. For example, `eval=FALSE` (do not evaluate code):

```{r test-eval, engine='python', eval=FALSE, ref.label='test-python'}
```

or `echo=FALSE` (hide source code):

```{r test-echo, engine='python', echo=FALSE, ref.label='test-python'}
```

or `results='hide'`:

```{r test-hide, engine='python', results='hide', ref.label='test-python'}
```

or `results='asis'`:

```{r test-asis, engine='python', results='asis'}
print '**Write** _something_ in `Markdown` from `Python`!'
```

## Strict Markdown

You can use strict markdown (i.e. indent by 4 spaces) by setting `render_markdown(TRUE)`.

```{r strict-markdown}
render_markdown(TRUE)
```

Now see how the output is changed:

```{r test-py-again, ref.label='test-python', engine='python'}
```
