# A Knitr "Polyglot" Example for Markdown

This is a minimal example of using "polyglot"" **knitr** to produce an _HTML_ page from _Markdown_.

```{r setup, echo=FALSE}
opts_chunk$set(fig.width=7, fig.height=5, echo=FALSE)
toTest <- c("R", "python", "scala", "bash")
where <- Sys.which(toTest)
exists <- nchar(where) > 0 # TODO: Only run chunk if runtime exists
```

## Engine runtime paths

```{r list-engines, results='asis'}
for(n in names(where)) {
  path <- where[n]
  if(nchar(path) <= 0) {
    path <- "<not found>"
  }
  cat("* __", n, "__: `", path, "`\n", sep="")
}
```

## Input Data
Pass the string to transform to engine subprocess via environment variable.

```{r, echo=TRUE}
Sys.setenv(SOMETHING = "something")
```

## Compute Something in R

```{r something-in-R, engine='R', comment='R>'}
something <- Sys.getenv("SOMETHING")
somethingmore <- strsplit(something, "")
somethingelse <- paste(sample(somethingmore[[1]]), collapse="")
cat(paste("'", something, "' is now '", somethingelse, "'", sep=""))
```

## Compute Something in Scala

Running small fragments without caching can take some time, as the Scala compiler has to launch and compile the script to JVM bytecode. The `-savecompiled` option (passed via `engine.opts`) will result in Scala caching the compiled script outside of _knitr_.

```{r something-in-Scala, engine='scala', comment='Scala>', engine.opts='-savecompiled', cache=TRUE}
import scala.util.Random._
val something = System.getenv("SOMETHING")
val somethingelse = shuffle(something.toSeq).mkString
println(s"'$something' is now '$somethingelse'")
```

## Compute Something in Python

```{r something-in-Python, engine='python', comment='Python>'}
import random, os
something = os.getenv("SOMETHING")
somethingmore = list(something)
random.shuffle(somethingmore)
somethingelse = ''.join(somethingmore)
print("'" + something + "' is now '" + somethingelse + "'")
```

## Compute Something in Bash

```{r something-in-Bash, engine='bash', comment='Bash>'}
something=$SOMETHING
somethingmore=$(echo $something | fold -w1)
somethingelse=$(for c in $somethingmore; do echo "$RANDOM $c"; done | sort -n | sed -e 's/^[0-9 ]*//' | paste -s -d '\0' -)
echo "'$something' is now '$somethingelse'"
```
