# A Minimal Example for Markdown

This is a minimal example of using **knitr** to produce an _HTML_ page from _Markdown_.

## Python code chunks

```{r setup}
# set global chunk options: images will be 7x5 inches
knitr::opts_chunk$set(fig.width=7, fig.height=5)
options(digits = 4)
```

Now we write some code chunks in this markdown file:

```{ipython computing}
x = 1+1 # a simple calculator
print(x)
from math import pi
print(pi)
import numpy as np
np.random.seed(123)
np.random.rand(5)  # boring random numbers
```

We can also produce plots:

```{ipython graphics}
import matplotlib.pyplot as plt
y = np.random.rand(20)
plt.hist(y)
plt.show()
```

## Inline code

Inline python code is also supported, e.g. the value of `x` is `ipython x`, and 2 &times; &pi;
= `ipython 2*pi`.

## Math

LaTeX math as usual: $f(\alpha, \beta) \propto x^{\alpha-1}(1-x)^{\beta-1}$.

## Misc

You can indent code chunks so they can nest within other environments such as lists.

1. the area of a circle with radius x
    ```{ipython foo}
    pi * x**2
    ```
2. OK, that is great

To compile me, use

```{r compile, eval=FALSE}
library(knitr)
knit('knitr-ipython.Rmd')
```

## Conclusion

Markdown is super easy to write. Go to **knitr** [homepage](http://yihui.name/knitr) for details.
